### 2014-05-29 paper/paper.tex
More modifications after first review.

\begin{figure} [!t]
	\begin{center}
	\includegraphics[scale=0.235]{img/moopDec.png}
	\caption{Decision and objective spaces in a MOP with two variables ($x_1$ and $x_2$) and two objectives ($f_1$ and $f_2$). In the objective space, yellow dots are non-optimal objective vectors, while blue dots form a non-dominated set.}
	\label{fig:moop}
	\end{center}
\end{figure}

@@

Extending this comparison to all maps, each pair of algorithms ends with a triplet $(D, \O, d)$, where $D$ is the number of maps where the first algorithm dominates the second, $\O$ is the amount of maps where no dominance can be established, and $d$ states the number of maps where the first is dominated by the second. Table~\ref{tab:resMOPTSP} summarizes these results for all the algorithms tested.

>>>>

\begin{figure} [!t]
	\begin{center}
	\includegraphics[scale=0.235]{img/moopDec2.png}
	\caption{Decision and objective spaces in a MOP with two variables ($x_1$ and $x_2$) and two objectives ($f_1$ and $f_2$). In the objective space, yellow dots are non-optimal objective vectors, while blue dots form a non-dominated set. From~\cite{Brockhoff2013}.}
	\label{fig:moop}
	\end{center}
\end{figure}

@@

Extending this comparison to all maps, each pair of algorithms ends with a triplet $(D, \O, d)$. $D$ is the number of maps where the first algorithm dominates the second. $\O$ is the amount of maps where no dominance can be established, either because the Mann-Whitney-Wilcoxon non-parametric test failed, or because there is no dominance according to the dominance rules described in Section~\ref{sec:moo}. Finally, $d$ states the number of maps where the first is dominated by the second. For example, a triplet $(D, \O, d) = (8,2,0)$ comparing algorithms $A$ and $B$ would mean that the results obtained by $A$ dominate those from $B$ in $8$ of the $10$ maps, and that it is not possible to derive any dominance in the other $2$. Table~\ref{tab:resMOPTSP} summarizes these results for all the algorithms tested.
